upwell_IDX

### 2020-04-21 upwell_IDX.Rmd
edits

# Combine and save
wind_data <- rbind(wind_fix_3, wind_fix_2, wind_fix_1)
save(wind_data, file = "Data/wind_data.RData")
load("Data/wind_data.RData")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay")

# RWS: Please figure out why some wind direction values are returned as NA
# RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# RWS: Please look through these resources and make corrections accordingly:
# https://cran.r-project.org/web/packages/rWind/rWind.pdf
# https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r
wind_daily <- wind_data %>%
  # ungroup() %>%
  # mutate(date = as.Date(date))%>% # Changing the date to date format
  filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
                                                           template = 'geographics')),2),  # Direction using the circular function
                  mean_speed = round(mean(speed),2)) # Calculating the mean

@@

# Plotting function
plot_sites <- function(site_list, buffer, dist){

>>>>

# Combine and save
wind_data <- rbind(wind_fix_3, wind_fix_2, wind_fix_1)
#save(wind_data, file = "Data/wind_data.RData")
# load("Data/wind_data.RData")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay")

# RWS: Please figure out why some wind direction values are returned as NA
# RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# RWS: Please look through these resources and make corrections accordingly:
# https://cran.r-project.org/web/packages/rWind/rWind.pdf
# https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r

wind_daily <- wind_data %>% 
  filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
                                                           template = 'geographics')),2),
                                    spw_circ = mean.circular(circular(speed, units = "degrees"))) # Direction using the circular function

@@

# Plotting function
# plot_sites <- function(site_list, buffer, dist){
